Supporting Information for ``Identifying regime transitions for water governance at a basin scale''

### 2023-05-15 paper/response_letter/source/editor.tex
feat(paper): :sparkles: 完成审稿人1的第一个意见修改
% 气候变化的确会产生很多影响，例如改变降水量和蒸发量。但这些影响都会以影响可用水量的形式体现在IWGI之中。 % 在新增加的图表中，我增加了天然水量的图表展示这种变化 % 例如气候变化让可用水量发生改变（scarcity），极端气候让我们难以有效的分配水资源（allocation），对气候变化的适应可能导致社会变革，让人们对愈发侧重于工业和经济发展的治理策略进行反思（priority）。 % 我们现在在讨论中涉及了这些话题。

Climate change is not explicitly represented in the index, which might play a key role in the streamflow recovery in the Yellow River in this century. Climate change would be a great challenge in the basin in the future. Significant climate change may affect the adaptive capacity of a basin and thus require different governance strategies.
fi

@@

\AR{} We acknowledge the need for a more in-depth analysis of our results. We have re-evaluated our data and expanded the results and discussion sections to include a deeper dive into the findings, specifically regarding the change points mentioned by both reviewers. We have also provided more context and explanation for these changes in the manuscript, which can be found on pages 14\-16 and 18\-21.

@@

\AR{} We agree with Reviewer \#2's suggestion to include a more thorough review of existing and relevant indicators with IWGI. We have added a new section in the manuscript discussing these indicators, comparing and contrasting their strengths and weaknesses, and explaining how our approach fills the gaps in the current literature. This new section can be found on pages 5\-7.

\subsection{Issue \#3}
\RC{} I would encourage the authors to look into more recent data (beyond 2013) as pointed out by Reviewer 1. In addition, I find the data in supplementary materials is not accessible, which should be amended. The data access and reproduction of the methodology/results are very important for WRR and our scientific community, so we take the issue related with data accessibility very seriously.

@@

\AR{} We appreciate the importance of using up-to-date data in our research. We have now included more recent data in our analysis, extending our dataset up to 2021. The updated data, along with the revised results and discussion, can be found on pages 11-13 and 18-21.

\AR*{} We apologize for the inconvenience caused by the inaccessibility of the supplementary materials. We have rectified this issue by ensuring that all supplementary data and files are now accessible and properly linked within the manuscript. We have also provided a clear description of the data and methodology in the supplementary materials to facilitate reproducibility of our results.

>>>>

\section{Associate Editor}\label{editor}

@@

\AR{} We acknowledge the need for a more in-depth analysis of our previous results. We have re-evaluated our data and expanded the results and discussion sections to include a deeper dive into the findings, specifically regarding the change points mentioned by both reviewers. We have also provided more context, explanation, and robustness analysis in the Supporting Informations (Section S2 to Section S4).

@@

\AR{} We agree with Reviewer \#2's suggestion to include a more thorough review of existing and relevant indicators with IWGI.\ We have added a new paragraph in the introduction discussing the existed indexes, comparing and contrasting their strengths and weaknesses, and explaining innovation of IWGI.\

\subsection{Issue \#3}
\RC{} I would encourage the authors to look into more recent data (beyond 2013) as pointed out by Reviewer 1. In addition, I find the data in Supporting Informations is not accessible, which should be amended. The data access and reproduction of the methodology/results are very important for WRR and our scientific community, so we take the issue related with data accessibility very seriously.

@@

\AR{} We appreciate the importance of using up-to-date data in our research. We have now included more recent data in our analysis.

\AR*{} We apologize for the inconvenience caused by the inaccessibility of the dataset. We have rectified this issue by refined our data description. Now, all the used datasets and their links are detailed described in the method section.

### 2023-05-15 paper/response_letter/source/reviewer_1.tex
refactor(paper): :recycle: 彻底梳理交叉图表引用

\subsection*{Overall comments} % todo

@@

\AR*{} In addition, we added a new graph (Figure~\ref{fig:runoff}~a) in the revised version of supplementary material to demonstrate the changes in runoff. Trend of natural runoff can also be inferred from the measured runoff (Figure~\ref{fig:runoff} from b to d) and water use (Figure~\ref{fig:runoff} from e to g). We quote this figure when discussing climate context, now:

\begin{quote}[page=10, sline=274, eline=277]
	% 一个基本背景是，在用水量总体保持稳定的情况下，黄河流域的径流量已显著低于从前，这是该时期水资源压力重新上升的重要原因。
	Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supplementary Materials Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
\end{quote}

@@

% 感谢您指出这一点，非常抱歉过于总结性的手稿带来的困惑。
% 在新的手稿中，我们将各指数的情况总结到补充材料，并在正文中对有关各指数情况的图表总结。
% 在方法中，我们补充了指标的取值范围（三个子指标的变化范围都是0～1）。
\AR{} Thank you for pointing this out, and we apologize for the confusion caused by the overly conclusive manuscript. In the revised manuscript, we have summarized the indicators by graphs with description in supplementary material:in the supplementary material.

% TODO 这里记得写一下是哪几个附图
\AR*{} Figure~\ref{fig:purpose} to Figure~\ref{fig:scarcity} are three indicators changing trends. We added them into supplementary materials with descriptions:

\begin{quote}[page=Supplementary Materials]
	The index of stress (SFV indicator, IS) in the study period (including three different periods) showed a change trend of first decreasing, then rapidly increasing, and finally slightly decreasing again (Figure~\ref{fig:scarcity}~A), indicating that water resource pressure first decreased, then rapidly increased, and then stabilized.
	Among the four different regions (Figure~\ref{fig:scarcity}~B), the source region (SR) has almost no contribution to IS changes in the three periods, and the downstream region (DR) only has a weak negative contribution in the governance transforming regime and the adaptation oriented regime.
	The upper and middle reaches (UR and MR) had the greatest impact on the IS changes. Wherein, the upper region (UR) made the greatest contribution during the massive supply regime and governance transforming regime, while the middle reaches made the greatest contribution in adaptation oriented regime.

	In terms of water use purpose indicator, IP remained basically unchanged in a massive supply regime, but showed a rapid decline in the period of governance transformation and adaptation oriented regime (Figure~\ref{fig:purpose}~A).
	Throughout the three periods, the change of irrigation water dominated the change of the IP, while urban and rural water for human settlements and rural livestock had almost no influence on the change of IP (Figure~\ref{fig:allocation}~B).

	The water allocation (IA) showed an obvious ``V-shaped'' trend, indicating that water resources in the different regions within the YRB first gradually moved away from uniform distribution, and then gradually tended to uniform distribution since 2000 (Figure~\ref{fig:allocation}).
\end{quote}

@@

% 感谢审稿人的宝贵建议，但出于以下原因，我们无法在新的手稿中将研究时段后延至今
\AR{} Thanks for the reviewer's valuable advice, but for the following reasons, we are unable to postpone the study period to date in the main text. Instead, we added robustness test by using different-source data in supplementary material.

@@

\begin{quote}[page=11, sline=325, eline=327]
	As a supplement, we examined IWGI framework with fewer datasets from different source in recent decades where showing no significant regime changes (supplementary Figure~\ref{fig:recent}).  % TODO 补充材料新图
\end{quote}

@@

\AR{} Yes, we did examination for the interconnections between the three indicators. Sorry we didn't make the information accessible. Now, we added a table to describe this in the supplementary material (Table~\ref{tab:corr}).

\input{source/tab_corr.tex}

\begin{quote}[page=Supplementary Materials]
	By analyzing the correlation of the integrated management index (IWGI) and its three sub-indexes: stress (IS), purpose (IP) and allocation (IA) in three different periods, namely, the massive supply regime (P1: $1965 \sim 1978$), governance transforming regime (P2: $1979 \sim 2001$) and adaptation oriented regime (P3: $2002 \sim 2013$), the following results are obtained.

@@

\AR*{} In addition, note that strictly independent of indicators is not required in our approach, as three aspects are intertwined in essence (we explained this in the introduction).
% 这是因为，如果两个子指标在某时期内相关性显著，可能说明两者在该时期同时受到某些治理驱动因素的共同作用，这是可能发生的。
This is because a significant correlation between two indicators in a given period may indicate that both were simultaneously affected by some governance drivers during that period, which is possible.
% 但同样，若两个指标始终都存在较强的关联，则可能说明稳态转换并不显著，IWGI同时考虑三者的意义也存疑。
Similarly, if there is always a strong correlation between the two indicators, it may indicate that the steady-state transformation is not significant, and the significance of IWGI considering the three indicators at the same time is doubtful.
% 然而，正如我们在表x中所展示的，IS, IP, IA三者两两之间的关系在不同稳态下都有不同的特征，这佐证了我们IWGI同时考虑三者的意义，以及稳态转换的存在。
However, as we have shown in Table~\ref{tab:corr}, the relationship between IS, IP and IA has different characteristics under different regimes, which proves that IWGI considers the significance of the three aspects at the same time, as well as the existence of regime shifts.

@@

% 我们检验过了年尺度的输水数据，基本变化不大
\AR*{} Finally, since we agree the conveyance is a good view to investigate water governance, we added an examination of the monthly conveyance flow differences of the major reservoirs and their variability in supplementary material. According to the Yellow River Water Conservancy Commission (YRCC, data source), these reservoirs are mainly for managing and regulating the whole basin. The result (Figure~\ref{fig:conveyance}) shows that variability increased in the later regimes, supporting our main results that regulation plays a more significant role since the governance transforming regime (P2). We also appropriately modified the description in main text:

\begin{quote}[page=8, sline=223, eline=225]
	Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~3~C, and larger water conveyance variability in Supplementary Materials Figure~S7).  % todo 检查图引用
\end{quote}

@@

\begin{quote}[page=2, sline=66, eline=77]
	Research into index-based water governance assessment generally fall into two categories: those that focus on water systems, and those that concentrate on governance systems.
	On one hand, studies on governance systems typically employ an qualitative assessment to demonstrate what practices influence water governance, e.g., the OECD framework~\cite{oecd2018a}.
	For quantitative studies, due to the lack of comprehensive and detailed information on key components for water governance assessment, these studies often resort to proxy datasets of human activities to create simpler indices~\cite{varis2019,huggins2020}.
	On the other hand, studies focusing on water systems utilize intuitive indices to encapsulate the outcomes of governance, like the most widely concerned -water stress has been far developed by incorporating human's regulation step by step.
	Specifically, traditional water stress index only demands and supply~\cite{gleick1996}, water scarcity index by involving storage~\cite{damkjaer2017}, and the even more integrated SFV-index includes flexibility~\cite{qin2019}.
	Despite their usefulness, these water stress indices tend not to provide a comprehensive characterization of water governance, as they overlook the social aspect of water usage, i.e., the purpose and allocation of water use.
	As a solution, we propose an integrated water governance index (IWGI) that factors in regional water use allocations and sectoral water use purpose, thereby offering a more comprehensive quantification of governance outcomes.
\end{quote}

@@

\AR{} That's a good suggestion. We now moved the calculation from supplementary material to the main text.

@@

\AR*{} We now attached a new supplementary material which includes descriptions and all sources of the datasets used in this study. If you want to know more about the data, please check the data source through the provided information.

@@

\AR{} We used $0.001$ for generating the figure at last (fixed the typo in Fig.2A now). Anyway, as we showed in supplementary material Figure~S3, no difference in results because the change points are robust. % TODO 检查一下鲁棒性的图表

>>>>

\subsection*{Overall comments}

@@

\AR*{} In addition, we added a new graph (Figure~\ref{fig:runoff}~a) in the revised version of Supporting Information to demonstrate the changes in runoff. Trend of natural runoff can also be inferred from the measured runoff (Figure~\ref{fig:runoff} from b to d) and water use (Figure~\ref{fig:runoff} from e to g). We quote this figure when discussing climate context, now:

\begin{figure}[!ht]
	\centering
	\renewcommand{\thefigure}{S2}
	\includegraphics[width=\textwidth]{sup/sf_measured_runoff.jpg}
	\caption{
		\textbf{a.} Measured runoff of different regions in the Yellow River Basin from 1965 to 2013.
		\textbf{b.} Measured runoff of different regions under different water governance regimes.
		\textbf{c.} Natural river runoff of different regions under different water governance regimes.
	}\label{fig:runoff}
\end{figure}

\begin{quote}[page=10, sline=274, eline=277]
	% 一个基本背景是，在用水量总体保持稳定的情况下，黄河流域的径流量已显著低于从前，这是该时期水资源压力重新上升的重要原因。
	Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supporting Informations Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
\end{quote}

@@

% 感谢您指出这一点，非常抱歉过于总结性的手稿带来的困惑。
% 在新的手稿中，我们将各指数的情况总结到补充材料，并在正文中对有关各指数情况的图表总结。
% 在方法中，我们补充了指标的取值范围（三个子指标的变化范围都是0～1）。
\AR{} Thank you for pointing this out, and we apologize for the confusion caused by the overly conclusive manuscript. In the revised manuscript, we have summarized the indicators by graphs with description in Supporting Information:in the Supporting Information.

\AR*{} Figure~S3, Figure~S4, and Figure~S5 are three indicators changing trends. We added them into Supporting Informations with descriptions:

\begin{figure}[!htb]
	\centering
	\renewcommand{\thefigure}{S5}
	\includegraphics[width=\textwidth]{sup/scarcity.png}
	\caption{Changing trend of the indicator of stress}\label{fig:scarcity}
\end{figure}

\begin{quote}[page=Supporting Informations]
	The index of stress (SFV indicator, IS) in the study period (including three different periods) showed a change trend of first decreasing, then rapidly increasing, and finally slightly decreasing again (Figure~\ref{fig:scarcity}~A), indicating that water resource pressure first decreased, then rapidly increased, and then stabilized.
	Among the four different regions (Figure~\ref{fig:scarcity}~B), the source region (SR) has almost no contribution to IS changes in the three periods, and the downstream region (DR) only has a weak negative contribution in the governance transforming regime and the adaptation oriented regime.
	The upper and middle reaches (UR and MR) had the greatest impact on the IS changes. Wherein, the upper region (UR) made the greatest contribution during the massive supply regime and governance transforming regime, while the middle reaches made the greatest contribution in adaptation oriented regime.
\end{quote}

\begin{figure}[!htb]
	\centering
	\renewcommand{\thefigure}{S3}
	\includegraphics[width=\textwidth]{sup/priority.jpg}
	\caption{Changing trend of the indicator of purpose}\label{fig:purpose}
\end{figure}

\begin{quote}[page=Supporting Informations]
	In terms of water use purpose indicator, IP remained basically unchanged in a massive supply regime, but showed a rapid decline in the period of governance transformation and adaptation oriented regime (Figure~\ref{fig:purpose}~A).
	Throughout the three periods, the change of irrigation water dominated the change of the IP, while urban and rural water for human settlements and rural livestock had almost no influence on the change of IP (Figure~\ref{fig:purpose}).
\end{quote}

\begin{figure}[!htb]
	\centering
	\renewcommand{\thefigure}{S4}
	\includegraphics[width=0.7\textwidth]{sup/allocation.png}
	\caption{Changing trend of the indicator of allocation}\label{fig:allocation}
\end{figure}

\begin{quote}[page=Supporting Informations]
	The water allocation (IA) showed an obvious ``V-shaped'' trend, indicating that water resources in the different regions within the YRB first gradually moved away from uniform distribution, and then gradually tended to uniform distribution since 2000 (Figure~\ref{fig:allocation}).
\end{quote}

@@

% 感谢审稿人的宝贵建议，但出于以下原因，我们无法在新的手稿中将研究时段后延至今
\AR{} Thanks for the reviewer's valuable advice, but for the following reasons, we are unable to postpone the study period to date in the main text. Instead, we added robustness test by using different-source data in Supporting Information.

@@

\begin{figure}[!htb]
	\centering
	\renewcommand{\thefigure}{S9}
	\includegraphics[width=0.8\textwidth]{sup/robustness.png}
	\caption{Recent years' IWGI changes}\label{fig:recent}
\end{figure}

\begin{quote}[page=11, sline=325, eline=327]
	As a supplement, we examined IWGI framework with fewer datasets from different source in recent decades where showing no significant regime changes (Supporting Informations~S9).
\end{quote}

@@

\AR{} Yes, we did examination for the interconnections between the three indicators. Sorry we didn't make the information accessible. Now, we added a table to describe this in the Supporting Information (Table~S1).

\input{../sup/tab_corr.tex}

\begin{quote}[page=Supporting Informations]
	By analyzing the correlation of the integrated management index (IWGI) and its three sub-indexes: stress (IS), purpose (IP) and allocation (IA) in three different periods, namely, the massive supply regime (P1: $1965 \sim 1978$), governance transforming regime (P2: $1979 \sim 2001$) and adaptation oriented regime (P3: $2002 \sim 2013$), the following results are obtained.

@@

\AR*{} In addition, note that strictly independent of indicators is not required in our approach, as three aspects are intertwined in essence (we explained this in the introduction).
% 这是因为，如果两个子指标在某时期内相关性显著，可能说明两者在该时期同时受到某些治理驱动因素的共同作用，这是可能发生的。
This is because a significant correlation between two indicators in a given period may indicate that both were simultaneously affected by some governance drivers during that period, which is possible.
% 但同样，若两个指标始终都存在较强的关联，则可能说明稳态转换并不显著，IWGI同时考虑三者的意义也存疑。
Similarly, if there is always a strong correlation between the two indicators, it may indicate that the steady-state transformation is not significant, and the significance of IWGI considering the three indicators at the same time is doubtful.
% 然而，正如我们在表x中所展示的，IS, IP, IA三者两两之间的关系在不同稳态下都有不同的特征，这佐证了我们IWGI同时考虑三者的意义，以及稳态转换的存在。
However, as we have shown in Table~S1, the relationship between IS, IP and IA has different characteristics under different regimes, which proves that IWGI considers the significance of the three aspects at the same time, as well as the existence of regime shifts.

@@

% 我们检验过了年尺度的输水数据，基本变化不大
\AR*{} Finally, since we agree the conveyance is a good view to investigate water governance, we added an examination of the monthly conveyance flow differences of the major reservoirs and their variability in Supporting Information. According to the Yellow River Water Conservancy Commission (YRCC, data source), these reservoirs are mainly for managing and regulating the whole basin. The result (Figure~\ref{fig:conveyance}) shows that variability increased in the later regimes, supporting our main results that regulation plays a more significant role since the governance transforming regime (P2). We also appropriately modified the description in main text:

\begin{figure}[!htb]
	\centering
	\renewcommand{\thefigure}{S8}
	\includegraphics[width=0.8\textwidth]{sup/conveyance.png}
	\caption{Monthly conveyance flow differences of the reservoirs mainly for managing and regulating the whole basin and their variability}\label{fig:conveyance}
\end{figure}

\begin{quote}[page=8, sline=223, eline=225]
	Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~3~C, and larger water conveyance variability in Supporting Informations Figure~\ref{fig:conveyance}).
\end{quote}

@@

\begin{quote}[page=2, sline=66, eline=77]
	Research into index-based water governance assessment generally fall into two categories: those that focus on water systems, and those that concentrate on governance systems.
	On one hand, studies on governance systems typically employ an qualitative assessment to demonstrate what practices influence water governance, e.g., the OECD framework~\cite{oecd2018a}.
	For quantitative studies, due to the lack of comprehensive and detailed information on key components for water governance assessment, these studies often resort to proxy datasets of human activities to create simpler indices~\cite{varis2019,huggins2022a}.
	On the other hand, studies focusing on water systems utilize intuitive indices to encapsulate the outcomes of governance, like the most widely concerned -water stress has been far developed by incorporating human's regulation step by step.
	Specifically, traditional water stress index only demands and supply~\cite{gleick1996}, water scarcity index by involving storage~\cite{damkjaer2017}, and the even more integrated SFV-index includes flexibility~\cite{qin2019}.
	Despite their usefulness, these water stress indices tend not to provide a comprehensive characterization of water governance, as they overlook the social aspect of water usage, i.e., the purpose and allocation of water use.
	As a solution, we propose an integrated water governance index (IWGI) that factors in regional water use allocations and sectoral water use purpose, thereby offering a more comprehensive quantification of governance outcomes.
\end{quote}

@@

\AR{} That's a good suggestion. We now moved the calculation from Supporting Information to the main text.

@@

\AR*{} We now attached a new Supporting Information which includes descriptions and all sources of the datasets used in this study. If you want to know more about the data, please check the data source through the provided information.

@@

\AR{} We used $0.001$ for generating the figure at last (fixed the typo in Fig.2A now). Anyway, as we showed in Supporting Information Figure~S7, no difference in results because the change points are robust.

### 2023-05-15 paper/response_letter/source/reviewer_2.tex
refactor(paper): :recycle: 彻底梳理交叉图表引用

\AR{} Thanks!

@@

\begin{quote}[page=2, sline=60, eline=77]
    Research into index-based water governance assessment generally fall into two categories: those that focus on water systems, and those that concentrate on governance systems.
    On one hand, studies on governance systems typically employ an qualitative assessment to demonstrate what practices influence water governance, e.g., the OECD framework~\cite{oecd2018a}.
    For quantitative studies, due to the lack of comprehensive and detailed information on key components for water governance assessment, these studies often resort to proxy datasets of human activities to create simpler indices~\cite{varis2019,huggins2020}.
    On the other hand, studies focusing on water systems utilize intuitive indices to encapsulate the outcomes of governance, like the most widely concerned -water stress has been far developed by incorporating human's regulation step by step.
    Specifically, traditional water stress index only demands and supply~\cite{gleick1996}, water scarcity index by involving storage~\cite{damkjaer2017}, and the even more integrated SFV-index includes flexibility~\cite{qin2019}.
    Despite their usefulness, these water stress indices tend not to provide a comprehensive characterization of water governance, as they overlook the social aspect of water usage, i.e., the purpose and allocation of water use.
    As a solution, we propose an integrated water governance index (IWGI) that factors in regional water use allocations and sectoral water use purpose, thereby offering a more comprehensive quantification of governance outcomes.
\end{quote}

@@

\AR*{} To make that more explicit, we modified the corresponding description in the Supplementary Materials:

\begin{quote}[page=Supplementary Materials]
    In addition, for capturing more specific water governance practices in the YRB had been recorded in ``Yellow River Events'' by the YRCC;\ we collected these documents from \url{http://www.yrcc.gov.cn/hhyl/hhjs/}.
    The original documents of those ``Events'' come from the Yellow River Conservancy Commission (YRCC), the agency that manages the YRB, which records and compiles ``major events'' related to the river. This study only recorded the number of these ``events'' year by year according to the time they occurred.
\end{quote}

@@

\begin{quote}[page=Supplementary Materials]
    Transition schema in hydrosocial cycle and water governance regimes. The natural water cycle dominates blue pathways, while socio-economic feedback dominates red.
    The large circular arrows indicate the social and hydrological processes that dominate in different stages.
    Provisioning water includes water used by human, livestock and crops while non-provisioning water includes used by industry and service.
    The processes expressed in the graph mainly include: Water supports people in provisioning ways or influence/influenced socioeconomic systems as non-provisioning ways; People manage/govern water system based on their well-beings.
    The gray thick arrow represents weaker process, while the red arrow represents more significant one.
\end{quote}

>>>>

\AR{} We appreciate your acknowledgement of the reasonable and adaptable methodology used in this study, as well as the useful insights provided by the case analysis. We agree that the discussion could be more supportive and solid in its content of the results and we will work to revise the manuscript accordingly. Please find our point-by-point response to your specific comments below.

@@

\begin{quote}[page=2, sline=60, eline=77]
    Research into index-based water governance assessment generally fall into two categories: those that focus on water systems, and those that concentrate on governance systems.
    On one hand, studies on governance systems typically employ an qualitative assessment to demonstrate what practices influence water governance, e.g., the OECD framework~\cite{oecd2018a}.
    For quantitative studies, due to the lack of comprehensive and detailed information on key components for water governance assessment, these studies often resort to proxy datasets of human activities to create simpler indices~\cite{varis2019,huggins2022a}.
    On the other hand, studies focusing on water systems utilize intuitive indices to encapsulate the outcomes of governance, like the most widely concerned -water stress has been far developed by incorporating human's regulation step by step.
    Specifically, traditional water stress index only demands and supply~\cite{gleick1996}, water scarcity index by involving storage~\cite{damkjaer2017}, and the even more integrated SFV-index includes flexibility~\cite{qin2019}.
    Despite their usefulness, these water stress indices tend not to provide a comprehensive characterization of water governance, as they overlook the social aspect of water usage, i.e., the purpose and allocation of water use.
    As a solution, we propose an integrated water governance index (IWGI) that factors in regional water use allocations and sectoral water use purpose, thereby offering a more comprehensive quantification of governance outcomes.
\end{quote}

@@

\AR*{} To make that more explicit, we modified the corresponding description in the Supporting Informations:

\begin{quote}[page=Supporting Informations]
    In addition, for capturing more specific water governance practices in the YRB had been recorded in ``Yellow River Events'' by the YRCC;\ we collected these documents from \url{http://www.yrcc.gov.cn/hhyl/hhjs/}.
    The original documents of those ``Events'' come from the Yellow River Conservancy Commission (YRCC), the agency that manages the YRB, which records and compiles ``major events'' related to the river. This study only recorded the number of these ``events'' year by year according to the time they occurred.
\end{quote}

@@

\begin{quote}[page=Supporting Informations]
    Transition schema in hydrosocial cycle and water governance regimes. The natural water cycle dominates blue pathways, while socio-economic feedback dominates red.
    The large circular arrows indicate the social and hydrological processes that dominate in different stages.
    Provisioning water includes water used by human, livestock and crops while non-provisioning water includes used by industry and service.
    The processes expressed in the graph mainly include: Water supports people in provisioning ways or influence/influenced socioeconomic systems as non-provisioning ways; People manage/govern water system based on their well-beings.
    The gray thick arrow represents weaker process, while the red arrow represents more significant one.
\end{quote}

### 2023-05-15 paper/sup/01_yrb.tex
refactor(paper): :recycle: 彻底梳理交叉图表引用

When calculating the indicators of IS and IA in this study (the SFV-index and the allocation entropy metric), we need consider data at a regional scale.
The YRB can be divided into four regions to calculate the indicators considering both socio-economic and natural conditions.
The division aligns with the customary schema from publications and the YRCC~\cite{yellowriverwaterconservancycommission2010,wang2019c}.

@@

>>>>

When calculating the indicators of IS and IA in this study (the SFV-index and the allocation entropy metric), we need consider data at a regional scale.
The YRB can be divided into four regions to calculate the indicators considering both socio-economic and natural conditions.
The division aligns with the customary schema from publications and the YRCC~\cite{yellowriverwaterconservancycommission2010,wang2019c}, hydrological characteristics are described in Figure~\ref{fig:runoff}.

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width=\textwidth]{sup/sf_measured_runoff.jpg}
	\caption{
		\textbf{a.} Measured runoff of different regions in the Yellow River Basin from 1965 to 2013.
		\textbf{b.} Measured runoff of different regions under different water governance regimes.
		\textbf{c.} Natural river runoff of different regions under different water governance regimes.
	}\label{fig:runoff}
\end{figure}

### 2023-05-15 paper/sup/02_indicator.tex
refactor(paper): :recycle: 彻底梳理交叉图表引用

\begin{figure}[!htb]
    \centering
    \includegraphics[width=\textwidth]{sup/priority.jpg}
    \caption{Changing trend of the indicator of purpose}\label{fig:purpose}
\end{figure}

@@

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.8\textwidth]{sup/allocation.png}
    \caption{Changing trend of the indicator of allocation}\label{fig:allocation}
\end{figure}

>>>>

\begin{figure}[!htb]
    \centering
    \includegraphics[width=\textwidth]{sup/priority.jpg}
    \caption{
        \textbf{left} Changing trend of the indicator of purpose (IP)
        \textbf{right} contributions of different water use sectors to the IS's changes.
    }\label{fig:purpose}
\end{figure}

@@

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.8\textwidth]{sup/allocation.png}
    \caption{Changing trend of the indicator of allocation (IA)}\label{fig:allocation}
\end{figure}

### 2023-05-15 paper/sup/04_robustness.tex
refactor(paper): :recycle: 彻底梳理交叉图表引用

@@

>>>>

Last, we tried our best to strengthen the period of this study despite the limitations of time span of the multiple-source dataset. We calculated the IWGI from 2003 to 2017 by using data from Yellow River Water Resources Bulletin to extend the study period. Since our results suggest no significant regime change (Figure~\ref{fig:recent}), we think it is robust that the YRB experienced two significant water governance regime changes in 1978 and 2001, without further changing since 21th century.

@@

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.8\textwidth]{sup/robustness.png}
	\caption{Recent years' IWGI changes calculated by data from Yellow River Water Resources Bulletin. No significant changing point exists}\label{fig:recent}
\end{figure}
